Correctly Optimizing Abstract Abstract Machines

### 2013-03-29 paper/paper.tex
Space saving.

\paragraph{Option 2: Regain precision; complicate implementation}
The administrative nature of laziness means that we could remove the
loss in precision by storing the result of the lookup in a value
representing a delayed nondeterministic choice. This has problems with
the next optimization, leading to unsoundness. Regaining soundness
would involve artificial complications to the semantics.

\paragraph{Our choice: option 1}
The configurations that lead to precision loss happen too rarely to
warrant the significant increase in time and memory needed for this
eager non-determinism. Without a widened store, lazy
non-determinism is not a complete abstraction with either approach,
but the precision gains are not immediately apparent due to fake
rebinding (a second reference to the same variable chooses a different
value from the first) and other problems. The performance and memory
gains are apparent, so we favor the simplicity over invisible
gains.}{}

>>>>

\paragraph{Option 2: Regain precision; complicate implementation}
The administrative nature of laziness means that we could remove the
loss in precision by duplicating the reduction relation to specialize
variable lookup. This works since in the semantics of ISWIM with
store-allocated results consumes the value component of states in one
step. This is not the case for semantics that replicate the value
component across reductions, say for popping off exception handler
frames. Further convolution is needed to remove the administrative
nature of laziness in these semantics. Due to the increase of
conceptual and implementation complexity for negligible benefit, we
decided against this approach.

\paragraph{Our choice: option 1}
The configurations that lead to precision loss happen too rarely to
warrant the significant increase in time and memory needed for this
eager non-determinism. Indeed, were the variable reference a step
later and another binding not made in that step, the results of the
two approaches are the same. Without a widened store, lazy
non-determinism is not a complete abstraction with either approach,
but the precision gains are not immediately apparent due to fake
rebinding (a second reference to the same variable chooses a different
value from the first) and other problems. The performance and memory
gains are apparent, so we favor the simplicity over invisible
gains.}{}
